From clusters to queries: exploiting uncertainty in the modular landscape of complex networks

### 2018-03-26 article/article.tex
Added boilerplate to article. But looks like I need to redo the analysis

\subsubsection{LFR benchmarks}

>>>>

\subsubsection{LFR benchmarks}
In this section we test the area under the ROC curve (AUC) scores for networks synthetically generated with the LFR benchmark.
The community distribution is defined with a powerlaw coefficient of $-1.0$ and the degree distribution is defined with a powerlaw coefficient of $-2.0$.
\textbf{Non-overlapping modules.} Figure \ref{fig:auc_no_overlap} represents tests on 100 networks with different randomly selected seed nodes.
As one would expect, the prediction of the method drops off steeply where communities are less defined above a mixing coefficient of 0.6.
Using larger seed sets also improves accuracy with some prediction of true communities being possible at extremely high levels of mixing.

\begin{figure*}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc.eps}
        \caption{1000 nodes}
    \end{subfigure}

    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc.eps}
        \caption{5000 nodes}
    \end{subfigure}
    \caption{Non-overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
     Data points represent mean auc scores for all communities on 100 sampled networks at varying mixing coefficients.
     Error bars represent standard deviations.}
\end{figure*}
